\documentclass[main.tex]{subfiles}
\begin{document}

What causes innovation? I'd argue there are two main causes: some fella is interested in a certain field, and as this person plays around new things are invented (such as the Linux kernel); the other is an extrinsic force, such as war, that encourages innovation. If we look at WW2, you can see numerous technologies developed. As fun as Turing's adventures in code-breaking were, I'm sure the extrinsic force is still largely to thank for breaking the Enigma Code. This is great, but sponsoring war as a way to bring about innovation isn't tempting, so let's look further. Exploration is another extrinsic force, whether we're looking at the sails to the New World or the Race to the Moon, these adventures pushed people to innovate. There's a whole Wikipedia page about “NASA Spinoff Technologies”\textsuperscript{1}. Obviously, the moon wasn't an independent focus, there was also the primary motivation to stick it to the commies that pushed the program. Even with the Cold War behind us, I'm sure that a program to Mars can still be viable. There is a fair amount of public interest and as a potential program develops, more people may become captivated by it. This increased public attention can cause major corporations, such as Google, to sponsor the movement, whether financially or by providing technologies. There are myriad problems that need to be addressed before jumping on a rocket to Mars, and these problems may bring about solutions that can be applicable to Earth. Limited area for agriculture on Mars, let's solve it by running an optimization program on a quantum computer that can yield a new system of agriculture. Mars has been given plants and Earth has fewer hungry people. Who knows what technologies are waiting just over the horizon that we need a slight push to develop. These technologies may be revolutionary or just make life more comfortable. Either way, we don't know what will come of it if we don't try. For the sake of brevity (and potentially a lack of imagination), I won't go through all the potential ways a Mars trip can lead to technologies that are applicable to life on Earth. Needless to say, the probability that a trip to Mars will produce at least one useful technology for Earth is very high.

\end{document}